% -*- root: Proposal.tex -*-
\documentclass[Proposal.tex]{subfiles} 
\begin{document}

\paragraph{Area A: Applicable mathematics.}
DPG is a method built on rigorous mathematical theory.
While rooted in the standard theory of finite elements, DPG is novel enough that many of the old analysis tools do not directly apply.
As a consequence, much of the early DPG literature has been laden with mathematical proofs of stability, convergence, and robustness.
While developing the theory for a locally conservative DPG formulation we performed a stability and robustness analysis.
Another robustness analysis will be necessary as we explore space-time convection-diffusion since the equation parabolic in space-time.
Past DPG robustness analysis focused on purely elliptic problems.

One significant remaining obstacle to obtaining robust solutions for compressible Navier-Stokes is guaranteeing positivity of the density and
energy in the presence of unresolved shocks. 
Positivity is an auxiliary stability condition that is not guaranteed by traditional stabilization 
techniques (including DPG), so it we are going to need to augment an additional technology to the method in order to guarantee physically
realizable densities and energies. 
Unfortunately, positivity preservation is itself an incredibly difficult problem. 
We have several ideas we want to try in the context of DPG, but solving the issue may not lie within the scope of this dissertation.

\paragraph{Area B: Numerical analysis and scientific computation.}
I will support development of the DPG software framework \emph{Camellia}\cite{Roberts2011} including running verification on several test problems.
This will include the development and verification of spatially 2D space-time simulations.
I will also develop a means to perform time stepping via space-time slabs which should reduce the 
overall run time and memory requirements for longer simulations.
I've already contributed several auxiliary features to \emph{Camellia} including mesh readers and solution export, 
but I also plan on looking into adding HDF5 support along with parallel solution output.

A space-time implementation adds additional dimensionality to the problem under consideration increasing the problem size and memory requirements.
This makes parallel simulation an increasingly important aspect of this work.
The 16 core \emph{Nozomi} cluster is sufficient for early experimentation, but as we ramp up to larger problems, I plan to run on allocations at TACC and on Mira at Argonne National Laboratory.

The major bottleneck to parallel simulations at the moment is that \emph{Camellia} still relies on a serial direct solver for the global solve.
Time permitting, I would like to investigate the implementation of an effective iterative solver for DPG.

\paragraph{Area C: Mathematical modeling and applications.}
As we are exploring a method that is still very much in development, I will be running a number of standard test problems.
I've already explored the conservation properties of DPG through a couple of simulations of Stokes flow around a cylinder and over
a backward facing step.

The steady state DPG formulation failed to converge on the Carter plate problem for Reynolds numbers of $10^7$. 
One hypothesis is that this was due to transient effects on the unresolved mesh which pushed the time step requirements very low.
The hope is that by using a space-time formulation with temporal adaptivity, we would be able to resolve these temporal oscillations
and they would die away to the correct steady state solution.
Another hypothesis is that the non-convergence was caused by Gibbs phenomenon near the unresolved leading edge driving the density negative.
Our line search algorithm scales the Newton updates to prevent negative densities, but sometimes the lines search factor can be driven so small
as to effectively stall convergence.
Therefore my first priority will be to investigate which factor is stalling convergence and attempt to solve it either via adaptive space-time
refinements or some sort of positivity preserving technology yet to be decided upon.
If this proves to be an effective way of handling transient shock problems, 
I would also like to simulate the Sedov explosion problem and the Noh implosion problem.
Time permitting, I would also like to run the triple point shock interaction problem and a Rayleigh-Taylor instability problem.
These will be ideal for demonstrating the local adaptivity of DPG.

That said, I believe that the most promising application for space-time DPG will be the incompressible Navier-Stokes equations.
Here we don't run into any of the same issues with Gibbs phenomenon and we can use vanilla space-time DPG.
The Taylor-Green vortex problem is an obvious choice since it has a exact solution that we can compare to.
There are several vortex shedding problems that would be of interest including flow over a triangle, square, and cylinder.

\end{document}