\documentclass{article}
\input{../preamble.tex}
\usepackage[margin=1.25in]{geometry}

\title{DPG for Engineers}
\author{Truman E. Ellis, Jesse L. Chan, Leszek F. Demkowicz, Jay Gopalakrishnan}

\begin{document}
\maketitle

\begin{abstract}
We discuss and explain the discontinuous Petrov-Galerkin finite element method with an engineering audience in mind.
\end{abstract}

\section{Motivation and Introductory Concepts}
The discontinuous Petrov-Galerkin finite element method is a promising new framework 
for automated computing of a broad class of partial differential equations.

\subsection{A Framework for Automated Computing}
% Stability => Multiphysics
% Stability => Easy meshing

\subsection{Mathematical Fundamentals}

\subsubsection{Banach, Hilbert, and Sobolev Spaces}
% Basic explanation with examples
Consider a bounded domain, $\Omega\in\mathbb{R}^d$ and a vector space of functions defined on $\Omega$.
A Banach space is a complete normed vector space.
An example of which is $L_1(\Omega)$ which is the set of all functions defined on $\Omega$ such that the $L_1$ norm
$\norm{u}_{L_1(\Omega)}:=\int_\Omega|u|$ is finite.
A Hilbert space is a Banach space where the norm is defined through an inner product.
An example of which is $L_2(\Omega)$ for which the norm is
$\norm{u}_{L_2(\Omega)}:=\LRp{u,u}_{L_2(\Omega)}^{\frac{1}{2}}:=\LRp{\int_\Omega u^2}^{\frac{1}{2}}$.
Finally, a Sobolev space is a Hilbert space where the inner product contains derivatives of the function.
A common Sobolev space is $H^1(\Omega)$ where $\norm{u}_{H^1(\Omega)}^2:=\norm{u}_{L_2(\Omega)}^2+\norm{\Grad u}_{L_2(\Omega)}^2$.

\subsubsection{Variational Formulations, Dual Spaces, and Riesz Maps}
Consider a Banach space $U$. The dual space, $U'$ is the set of all linear functionals on $U$ such that the pairing $\LRa{u,w}_{U\times U'}\in\mathbb{R}$ 
for all $u\in U$ and $w\in U'$.
Any PDE problem can abstractly be written as: find solution $u\in U$ such that
\[
Bu=l
\]
where $B:U\rightarrow V'$ maps functions to some dual space and $l\in U'$.
By the calculus of variations, this is equivalent to the problem: find solution $u\in U$ such that
\[
\LRa{Bu,v}=\LRa{l,v}
\]
for all functions $v\in V$ and $v$ is called a test function.
This defines a bilinear form $b(u,v)=f(v)$ where $u$ is often called the trial function.
Now let $U$ and $V$ be Hilbert rather than merely Banach.
The Riesz representation theorem defines a bijective, isometric mapping from every member in $V$ to a corresponding member in the dual space $V'$.
We denote this mapping $R_V:V\rightarrow V'$.
Thus, we can take our operator equation representing the strong form of our PDE
\[
Bu-l=0\quad\in V'
\]
and map it back to $V$ via the inverse Riesz map:
\[
R_V^{-1}(Bu-l)=0\quad\in V.
\]

% \subsubsection{Broken Sobolev Spaces}
% Quick definition of Sobolev spaces

\subsection{Ritz Methods and Least Squares}

\subsection{SUPG -- Or Stability Through the Appropriate Test Space}

\section{Development of a DPG Method for the Poisson Equation}
% Start with a specific example then generalize
% Alternatively do convection-diffusion or reaction-diffusion

\section{DPG for Well Posed PDEs}

\end{document}